Sailing the High Seas: A Christian Exploration of Piracy

### 2024-04-24 paper.tex
Edit packages used.
Also add epigraph package for formatting

\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{footnote}
\usepackage{endnotes}
\usepackage[bottom, multiple]{footmisc}
\usepackage[level]{fmtcount}

\usepackage{float}
\usepackage{graphicx}
\usepackage{wrapfig}
\graphicspath{ {./graphics} }

@@

\makesavenoteenv{figure}
\SetCiteCommand{\cite}

@@

\begin{document}
\maketitle

\begin{refsection}

\section{Introduction}

\subsection{Background Information}
\blockcquote{barlow:wine}{%
  \textins{T}hat ideas should freely spread from one to another over the globe,
  for the moral and mutual instruction of man, and improvement of his
  condition, seems to have been peculiarly and benevolently designed by nature,
  when she made them, like fire, expansible over all space, without lessening
  their density at any point, and like the air in which we breathe, move, and
  have our physical being, incapable of confinement or exclusive appropriation.
  Inventions then cannot, in nature, be a subject of property.
  \emph{Thomas Jefferson}%
}

It is generally accepted that piracy is an illegal activity, but what is often overlooked
is the legitimate role that piracy plays in a variety of contexts. When it comes to
subverting oppressive regimes, for instance, the tools that piracy provides are
indispensable and for protecting the interests of consumers from predatory business
practices, the abilities of piracy are unmatched.

>>>>

\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{epigraph}
\usepackage{footnote}
\usepackage[bottom, multiple]{footmisc}

@@

\SetCiteCommand{\cite}

@@

\begin{document}
\begin{refsection}
\maketitle
\epigraph{%
  \textins{T}hat ideas should freely spread from one to another over the globe,
  for the moral and mutual instruction of man, and improvement of his
  condition, seems to have been peculiarly and benevolently designed by nature,
  when she made them, like fire, expansible over all space, without lessening
  their density at any point, and like the air in which we breathe, move, and
  have our physical being, incapable of confinement or exclusive appropriation.
  Inventions then cannot, in nature, be a subject of property.%
}{Thomas Jefferson~\cite{barlow:wine}}

\section{Introduction}
\subsection{Background Information}
It is generally accepted that piracy is an illegal activity, but what is often overlooked
is the legitimate role that piracy plays in a variety of contexts. When it comes to
subverting oppressive regimes, for instance, the tools that piracy provides are
indispensable and for protecting the interests of consumers from predatory business
practices, the abilities of piracy are unmatched.
